Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-02-02 causal-bandit/icml-2015/introduction.tex
minor updates

In the general casual model interventions and observations may have a complex relationship. 
In \S\ref{sec:simple-regret-general} we propose an algorithm (Algorithm~\ref{alg:alloc}) inspired by importance-sampling that a) enjoys sub-linear regret equivalent to the optimal rate in the parallel bandit setting and b) captures many of the intricacies of sharing information in a causal graph in the general case. 
As in the parallel bandit case, the regret guarantee is often significantly better than $O(\sqrt{N/T})$ and never worse, where $N$ is the number of available interventions.

>>>>

In the general casual model interventions and observations may have a complex relationship. 
In \S\ref{sec:simple-regret-general} we propose an novel algorithm inspired by importance-sampling that a) enjoys sub-linear regret equivalent to the optimal rate in the parallel bandit setting and b) captures many of the intricacies of sharing information in a causal graph in the general case. 
As in the parallel bandit case, the regret guarantee is often significantly better than $O(\sqrt{N/T})$ and never worse, where $N$ is the number of available interventions.
